\plaintitle

### 2025-04-30 docs/style/article-body.tex
pushing latest version

All iterations was tested on 6 different input datasets, with some results varying less than 0.1 microseconds. The results with such slight variations have been omitted from the table. All the tables shown below has been tested on the dataset `biased\_bits\_bad' which can be found as an appendix.

@@

The first iteration brought few surprises, as it ran quite well on Teensy. To our surprise, it executed well enough on Pi Pico 2 as well, albeit with \(~8\times\) slower execution speed.

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1000}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1583}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1583}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1583}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1417}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1417}}
  >{\raggedright\arraybackslash}p{(\linewidth - 12\tabcolsep) * \real{0.1417}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\textbf{Bit size}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Teensy Min (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Teensy Max (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Teensy Avg (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Pico Min (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Pico Max (µs)}
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\textbf{Pico Avg (µs)}
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
64 & 13 & 14 & 13.1564 & 103 & 117 & 106.3914 \\
512 & 788 & 791 & 788.3139 & 5296 & 5311 & 5302.4979 \\
1024 & 3124 & 3130 & 3124.0580 & 21108 & 21119 & 21111.2163 \\
\end{longtable}

>>>>

All iterations was tested on 6 different input datasets, with some results varying less than 0.1 microseconds. These results with such slight variations have been omitted from the table. All the tables shown below has been tested on the dataset \texttt{biased\_bits\_bad.bin} which can be found as an appendix -- and whereas more files have been used, this file has been arbitrarily selected to present the data.

@@

The first iteration brought few surprises, as it ran quite well on Teensy. To our surprise, it executed well enough on Pi Pico 2 as well, albeit with \textasciitilde{}\(8\times\) slower execution speed. This first implementation is the same one used to generate the baseline results, and used to ensure following iterations all generate correct output.

Worth noting is that this iteration (\_and all following iterations that generate the same result) have achieved entropy scores from \texttt{ent} that are greater than 7.99 for all tested data while ensuring it cannot be compressed further. This ensures that the algorithm has successfully removed as much of the patterns as can be reasonably expected from the raw binary data while maintaining the random nature of the data.

\centering

\begin{tabular}{|c|c|c|c|c|c|c|} \hline \textbf{Bit size} &
\multicolumn{3}{c|}{\textbf{Teensy (µs)}} & \multicolumn{3}{c|}{\textbf{Pico
(µs)}} \\ \hline & Min & Max & Avg & Min & Max & Avg \\ \hline 64 & 13 & 14 &
13.1564 & 103 & 117 & 106.3914 \\ 512 & 788 & 791 & 788.3139 & 5296 & 5311 &
5302.4979 \\ 1024 & 3124 & 3130 & 3124.0580 & 21108 & 21119 & 21111.2163 \\
\hline \end{tabular} \caption{Minimum, maximum and average processing time for
Teensy and Pico.} \label{tab:teensy_pico_min_max_avg}

\textbackslash end\{table\}
